Trends of SDR in Thessaloniki

### 2023-07-06 Article.Rmd
Commit 2023-07-06 22:14

```{r echo=F, include=T, warning=FALSE, message=FALSE}
res <- rmarkdown::find_pandoc(dir = '/usr/lib/rstudio/resources/app/bin/quarto/bin/tools')
## document configurations 
knitr::opts_chunk$set(comment    = ""      )
# knitr::opts_chunk$set(dev        = "pdf"   )
knitr::opts_chunk$set(out.width  = "70%"   )
knitr::opts_chunk$set(fig.align  = "center")
knitr::opts_chunk$set(fig.pos    = 'h!'    )
options(knitr.graphics.auto_pdf = FALSE)
library(pander)
library(data.table)
## load data
load("~/MANUSCRIPTS/2022_sdr_trends/data/common_data_14_2.Rda")
TSIinfo <- data.table(read.csv("~/MANUSCRIPTS/2022_sdr_trends/figures/tbl_tsi_info.dat",
                    strip.white = TRUE,
                    sep = ";",
                    header = TRUE))
## variables we use
source("~/MANUSCRIPTS/2022_sdr_trends/DHI_GHI_0_variables.R")

@@

suppressMessages(
    gather_citations(
        sourcefile   = "~/MANUSCRIPTS/2022_sdr_trends/Article.Rmd",
        mainreposit  = "~/MANUSCRIPTS/2022_sdr_trends/Mainreferences.bib",
        localreposit = "~/MANUSCRIPTS/2022_sdr_trends/references.bib",
        folderlink   = "~/MANUSCRIPTS/2022_sdr_trends/References_links",
        workingdir   = "~/MANUSCRIPTS/2022_sdr_trends/"
    )
)
```

>>>>

```{r echo=F, include=T, warning=FALSE, message=FALSE}
suppressMessages(
    res <- rmarkdown::find_pandoc(dir = '/usr/lib/rstudio/resources/app/bin/quarto/bin/tools')
)
## document configurations 
knitr::opts_chunk$set(comment    = ""      )
# knitr::opts_chunk$set(dev        = "pdf"   )
knitr::opts_chunk$set(out.width  = "70%"   )
knitr::opts_chunk$set(fig.align  = "center")
knitr::opts_chunk$set(fig.pos    = 'h!'    )
options(knitr.graphics.auto_pdf = FALSE)
library(pander)
library(data.table)
## load data
load("./data/common_data_14_2.Rda")
TSIinfo <- data.table(read.csv("./figures/tbl_tsi_info.dat",
                    strip.white = TRUE,
                    sep = ";",
                    header = TRUE))
## variables we use
source("./DHI_GHI_0_variables.R")

@@

suppressMessages(
    gather_citations(
        sourcefile   = "./Article.Rmd",
        mainreposit  = "./Mainreferences.bib",
        localreposit = "./references.bib",
        folderlink   = "./References_links",
        workingdir   = "./"
    )
)
```
